Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2024-02-05 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
Plot bias-mse legends modified

# use some specific Tex packages if needed. 
#with_ifpdf: true
#with_cite: true
# amsmath need to be true to use with bookdown for referencing equations.
with_amsmath: true
# with_algorithmic: true
# with_array: true
# with_dblfloatfix: true

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{mathtools}
   - \usepackage[utf8]{inputenc}
   - \usepackage{hyperref}
   - \hypersetup{draft}
   - \usepackage{graphicx}
   - \usepackage{float}
   - \usepackage{booktabs}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{xcolor}
   - \usepackage{amsmath}
   - \usepackage{mathabx}
   - \usepackage{subfig}
   #- \usepackage{subcaption}
   - \usepackage{pgf}
   - "\\setcitestyle{square,comma,numbers,sort&compress}" # citation style to numerical, work with \cite{} or [@]

@@

@@

#link-citations: yes

@@

@@

Simulations are conducted using $G_I^0$ distribution, with $500$ simulated samples of size \(n\in\left\{9, 25, 49, 81, 121\right\}\). For brevity, we present the results with \(\mu=1\), \(\alpha=-10\), and \(L=5\). The results are consistent for other values of the mean. 
In the case of the bootstrap technique, each sample is replicated $100$ times with replacement.
We choose to use the following heuristic formula for spacing, $m=\left[\sqrt{n}+0.5\right]$.

In Fig.&nbsp;\ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions. 
The use of the bootstrap technique exhibits more precision, reduced bias and MSE, and improved convergence.
<!-- ACF Show only the first line, i.e., for mu=1, and state that the results are consistent for other values of the mean -->

The results of simulation are exhibited in Table&nbsp;\ref{tab:table2}.
The precision of estimators, as evidenced by bias and MSE comparisons, benefits significantly from the bootstrap technique, particularly for sample sizes below 81.

@@

```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE of entropy estimators for  $G_I^0$, $L=5$, $\\alpha=-10$.", fig.width=6, fig.height=3.0}

@@

print(
  kbl(
    reshaped_results,
    caption = "Bias and MSE of bootstrap estimators for $G_I^0$, $L=5$, $\\alpha=-10$.",
    format = "latex",
    booktabs = TRUE,
    align = "lrrrrrrrr",
    escape = FALSE, 
    digits = 3,  
    label = "table2"
  ) %>%
    add_header_above(c(" ", " ", "Bias" = 3, "MSE" = 3)) %>%
    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
    row_spec(0,  align = "c")
    #kable_styling(latex_options = "hold_position", "scale_down")
  )

@@

```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Empirical density  under null hypothesis.", fig.width=6, fig.height=5}

@@

combined_plot <- wrap_plots(all_plots, ncol = 2, nrow = 2) +
  plot_layout(guides = "collect")

@@

table_result_combined <- kbl(
  combined_summary_stats,
  caption = "Descriptive analysis of $S(\\bm Z; L)$ with $L\\in\\left\\{2, 8\\right\\}$ and $\\mu=1$.",
  format = "latex",
  booktabs = TRUE,
  align = "lrrrrrrr",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined"
  #table.env = 'table*' # to span multiple columns
) %>%
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")

@@

## Application to Actual Data

We applied the test statistical to a SAR image of Flevoland, Netherlands, acquired by the Sentinel-1A system operating in the C band, with  HH polarization, intensity format, and $L=5$ nominal looks.
This image has $300 \times 300$ pixels and covers urban areas and agricultural fields. 
<!-- The metadata associated with these original SAR images includes a number of looks $L = 5$. -->

>>>>

# use some specific Tex packages if needed.

# amsmath need to be true to use with bookdown for referencing equations.
with_amsmath: true
#with_subfig:true

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{mathtools}
   - \usepackage[utf8]{inputenc}
   - \usepackage{hyperref}
   - \hypersetup{draft}
   - \usepackage{float}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{xcolor}
   - \usepackage{amsmath}
   - \usepackage{mathabx}
   - \usepackage{subfig}
   #- \usepackage{caption}
   #- \captionsetup[table]{skip=0pt}
   - "\\setcitestyle{square,comma,numbers,sort&compress}" # citation style to numerical, work with \cite{} or [@]

@@

    #extra_dependencies: "subfig"

@@

@@

\let\oldtablename\tablename
\renewcommand{\tablename}{\MakeUppercase{\oldtablename}}
\let\oldfigurename\figurename
\renewcommand{\figurename}{Fig.}

@@

Simulations are conducted using $G_I^0$ distribution, with $500$ simulated samples of size \(n\in\left\{9, 25, 49, 81, 121\right\}\). For brevity, we present the results with \(\mu=1\), \(\alpha=-10\), and \(L=5\). The results are consistent for other values of the mean. 
In the case of the bootstrap technique, each sample is replicated $100$ times with replacement.
We choose to use the following heuristic formula for spacing, $m=\left[\sqrt{n}+0.5\right]$.
<!-- ACF Show only the first line, i.e., for mu=1, and state that the results are consistent for other values of the mean -->

In Fig.&nbsp;\ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions. 
The use of the bootstrap technique exhibits more precision, reduced bias and MSE, and improved convergence.
The results of simulation are exhibited in Table&nbsp;\ref{tab:table2}.

The precision of estimators, as evidenced by bias and MSE comparisons, benefits significantly from the bootstrap technique, particularly for sample sizes below 81.

@@

```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE, $L=5$ and  $\\alpha=-10$.", fig.width=6, fig.height=3.0}

@@

print(
  kbl(
    reshaped_results,
    caption = "Bias and MSE of bootstrap estimators.",
    format = "latex",
    booktabs = TRUE,
    align = "lrrrrrrrr",
    escape = FALSE, 
    digits = 3,  
    label = "table2"
  ) %>%
    add_header_above(c(" ", " ", "Bias" = 3, "MSE" = 3)) %>%
    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
    row_spec(0,  align = "c")
    #kable_styling(latex_options = "hold_position", "scale_down")
  )

@@

```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Empirical density  under null hypothesis.", fig.width=6, fig.height=3.0}

@@

combined_plot <- wrap_plots(all_plots, ncol = 2, nrow = 1) +
  plot_layout(guides = "collect")

@@

table_result_combined <- kbl(
  combined_summary_stats,
  caption = "Descriptive analysis of $S(\\bm Z; L)$ with $L\\in\\left\\{2, 8\\right\\}$ and $\\mu=1$.",
  format = "latex",
  booktabs = TRUE,
  align = "lrrrrrrr",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined",
  #table.env = 'table*' # to span multiple columns
) %>%
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")

@@

## Application to Actual Data
We applied the test statistical to a SAR image of Flevoland, Netherlands, acquired by the Sentinel-1A system operating in the C band, with  HH polarization, intensity format, and $L=5$ nominal looks.
This image has $300 \times 300$ pixels and covers urban areas and agricultural fields. 
<!-- The metadata associated with these original SAR images includes a number of looks $L = 5$. -->
